Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-22 manuscript/manuscript.Rmd
single species comments on jitter

>>>>

There is a presence of certain high-mortality points at low $X$ values in the PPO policy (which in turn generates a rising fishing mortality for $X$ values below a certain threshold in the PPO+GP policy).
This is likely due to experience of near-extinctions early on in the training process---where, given an impending extinction, it is more rewardful to fish intensively. 
These ‘‘jitters’’ are likely not fully erased through the optimization algorithm since near-extinction events become extremely rare after only a few training iterations.
This way, the agent does not further explore that region of state space to generate new experience.
We believe the most important aspect of the constant escapement policy reproduced by PPO is the fact that there is some sufficiently-wide window below the threshold of the policy (i.e. below the optimal escapement value), on which no fishing is performed.
That is, there exists some sufficiently large $\varepsilon$ such that, if $X_{\text{thresh.}}$ is the optimal escapement value of the system, then $\pi_{PPO}(X)=0$ for all $X\in[X_{\text{thresh.}}-\varepsilon,\ X_{\text{thresh.}}]$.
